---
title: "ProsperityRound1"
output: rmarkdown::github_document
date: "2025-04-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Trade Objective
We’ve invited representatives from our neighboring islands to join us for the celebratory Archipelago Trade-Off. You can trade Snowballs with Pam the Penguin from the north, Pizza’s with Devin the Duck from the south, and Silicon Nuggets with Benny the Bull from the west archipelago.

Your objective is to trade these currencies and maximize your profit in SeaShells. The number of trades is limited to 5. You must begin your first trade and end your last trade with our own currency; SeaShells. Use the trading table to develop your trading strategy, and use the drop down fields to translate your strategy into actionable input. Once you are satisfied with your strategy and input, use the ‘Submit manual trade’ button to lock it in.

# Trading Table
```{r}
currency.names <- c("Snowballs", "Pizza's", "SiliconNuggets", "SeaShells")
(trading.mat <- matrix(c(1,0.7,1.95,1.34,1.45,1,3.1,1.98,0.52,0.31,1,0.64,0.72,0.48,1.49,1), nrow = 4, ncol = 4, dimnames = list(currency.names,currency.names)))
```
# Calculating
Number of trades is limited to 5, so all possible trades are listed below (last trade has to be SeaShells).
```{r}
possible.trades.mat <- as.matrix(expand.grid(1:4, 1:4, 1:4, 1:4,4))
head(possible.trades.mat)
```
Now we want to calculate the outcome based on a sequence.
```{r}
calc_outcome <- function(seq.of.trades) {
  last <- 4 #first Trade SeaShells
  multiplier <- sapply(seq.of.trades, function(x) {
    mult <- trading.mat[last, x]
    assign('last', x, inherits = TRUE)
    return(mult)
  })
  prod(multiplier)
}
```
We apply the ´calc_outcome´ function to each sequence.
```{r}
outcomes <- apply(possible.trades.mat, 1 , calc_outcome)
```
After getting the outcome for each sequence we search for the optimal sequence.
```{r}
optimal.seq <- currency.names[possible.trades.mat[which(outcomes == max(outcomes)),]]
paste0(c("SeaShells", optimal.seq), collapse = "->") #Starting with SeaShells
```


